\hypertarget{lightning-creations-lcsd-2---proposed-procedure-for-lcs-draft-and-lcs-document-review}{%
\section{Lightning Creations LCSD 2 - Proposed Procedure for LCS Draft
and LCS Document
Review}\label{lightning-creations-lcsd-2---proposed-procedure-for-lcs-draft-and-lcs-document-review}}

Draft Date: 2019-10-05

Copyright © 2019 Connor Horman and Lightning Creations. This document
may be freely copied and distributed but changing is not allowed, except
as explicitly licensed.

\hypertarget{d1-suggested-title}{%
\subsection{§D1 Suggested Title}\label{d1-suggested-title}}

As part of the proposal for this document, the Suggested Title for the
associated LCS Document is ``LCS 2 - Procedure for LCS Draft and LCS
Document''.

This document is proposed to receive the Document Number 2.

\hypertarget{lcs-review-committee}{%
\subsection{§1 LCS Review Committee}\label{lcs-review-committee}}

The LCS Review Committee is a group tasked by Lightning Creations with
the duty of Reviewing LCS Drafts to prepare them for publication, and
Reviewing Proposed LCS Documents before publishing them, as defined by
§3 of LCS 1.

This document defines the procedure which the LCS Review Committee shall
use to review LCS Drafts and Documents.

\hypertarget{status-of-this-publication}{%
\subsubsection{§1.1 Status of this
Publication}\label{status-of-this-publication}}

This Publication, as LCS 2, shall be considered an LCS Document. It
shall also be an agreement between all members of the LCS Review
Committee.

Annually, the LCS Review Committee shall subject this Publication to
Committee Review (§2.2). A Revision of this LCS Document may then be
published if changes are deemed necessary.

\hypertarget{d1-status-of-this-draft}{%
\subsubsection{§1.D1 Status of this
Draft}\label{d1-status-of-this-draft}}

This Draft, as Lightning Creations LCSD 2, shall be considered an LCS
Draft. It holds no standing outside of being an LCS Draft.

\hypertarget{review-processes}{%
\subsection{§2 Review Processes}\label{review-processes}}

This document defines 2 standardised review processes for use in
reviewing LCS Drafts and Documents. Under most circumstances, LCS Drafts
and Documents should be reviewed using one of these methods, however, at
the option of the LCS Review Committee, a separate process may be used
for any given LCS Draft or Document.

Each part of a Reviewed LCS Draft or Document should be considered as a
whole, and individually in the context of the LCS Draft or Document.
Each section of an LCS Draft or Document (Collectively ``Reviewed
Document'') should be clear, well-structured, and related to the subject
matter of the Reviewed Document. Additionally, each section of a
Reviewed Document should not have grammatical errors, or other issues
with the use of language. Judgements for the above fall to the Reviewer
in the case of Individual Review, and the LCS Review Committee in the
case of Committee Review.

\hypertarget{individual-review}{%
\subsubsection{§2.1 Individual Review}\label{individual-review}}

Any LCS Draft may be subjected to Individual Review. In such review of
an LCS Draft, a member of the LCS Review Committee is elected to serve
as the Reviewer. The Reviewer may request any number of additional
members to act as Review Advisers, who will assist the Reviewer in the
Individual Review.

The Reviewer will consider the LCS Draft as a whole, and its parts
individually in the context of the LCS Draft, and will either accept the
LCS Draft, request it be updated with comments on portions which need to
be fixed, or deny the LCS Draft.

If the Draft is denied, then no further review will take place. The
reviewer should provide detailed information as to the reasoning for the
denial.

If the Draft is accepted, the reviewer shall consult the LCS Review
Committee to assign the Draft a Document Number. The Draft Author should
then be requested to submit a ``Final Revision'', in the form of an LCS
Document, with that assigned Document number. When received, the ``Final
Revision'' shall be subject to Committee Review (defined below, §2.2),
and if accepted, will be published AS-IS as an LCS Document.

\hypertarget{conflict-of-interest}{%
\paragraph{§2.1.1 Conflict of Interest}\label{conflict-of-interest}}

Members of the LCS Review Committee may submit LCS Drafts of there own.
When an LCS Draft is subject to Individual Review, the Draft Author may
not serve as the Reviewer. The Draft Author may serve as an advisor for
the Reviewer. This is to prevent general bias in the Review process.

\hypertarget{committee-review}{%
\subsubsection{§2.2 Committee Review}\label{committee-review}}

LCS Drafts, and ``Final Revisions'' of LCS Documents may be subject to
Committee Review. Rather than an elected individual, all members of the
LCS Review Committee will Review the Draft or ``Final Revision'' as a
group. The same considerations as with Individual Review shall be made
towards any Draft or ``Final Revision'' in Committee Review. Whether or
not a Draft or ``Final Revision'' is accepted, denied, or revisions are
requested, is decided by a Majority vote of the LCS Review Committee. In
the event of a tie for majority, precedence will be given to Revision
Requests, then Denial, then Acceptance.

\hypertarget{review-of-lcs-1-lcs-2-and-all-other-special-lcs-documents}{%
\subsubsection{§2.3 Review of LCS 1, LCS 2, and all other special LCS
Documents}\label{review-of-lcs-1-lcs-2-and-all-other-special-lcs-documents}}

Some Special LCS Documents are subject, by a self-contained clause, to
Annual Committee Review. The Review of such LCS Documents cannot be
denied, only accepted AS-IS, or revisions requested. When Revisions of
such an LCS Document are requested, a member of the LCS Review Committee
is elected to author, on behalf of Lightning Creations, a Draft which
revises the LCS Document in question.

These Revisions shall then be subject to Committee Review, and when
accepted, the Revisions shall be published. The ``Final Revision''
process is skipped for such Drafts.

\hypertarget{drafts-authored-on-behalf-of-lightning-creations}{%
\subsubsection{§2.4 Drafts Authored on behalf of Lightning
Creations}\label{drafts-authored-on-behalf-of-lightning-creations}}

Members of Lightning Creations may Author LCS Drafts of behalf of
Lightning Creations. These Drafts shall be reviewed with strict
scrutiny. For purposes of Review, the Author of that Draft may be
considered the Member or Members of Lightning Creations whom submitted
the LCS Draft.

Additionally, LCS Drafts Authored on behalf of Lightning Creations shall
be reviewed specially for the purposes of determining the necessity of
scope. If it is determined that the draft's subject matter or content
does not warrant publication from Lightning Creations, it shall be
denied. Resubmissions of the draft may be accepted if made from the
original Author.

LCS Drafts revising Special LCS Documents pursuant to §2.3 shall be
exempted from these rules.
